Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-17 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
a comment to the Conclusions section

In general, linking and finding correlations between user choices and
performance is an interesting avenue to explore in the future. Even if
the three previous experiments were published in a similar, way, one
obtained up to 5 times more total cycles  that the one with the least
number of cycles. It is also essential to obtain volunteers as
simultaneously as possible, so it is possible that the features of the
social network in terms of real-time use will also play a big
role. Even as it is difficult to create controlled experiments in this
area, it is an interesting challenge to explore in the future.

Although we think that, in general, the results presented in this
paper are independent of the problem chosen, it is true that even if
it is a difficult problem for evolutionary algorithms, it takes a few
seconds with the right settings to solve. This makes it difficult also
for this kind of asynchronous framework, but it would be interesting
to check the performance for more computationally demanding
tasks. Besides, the two versions of the framework include as an
algorithmic variant using random population size. We do not think this
has had a big influence on the result, but it would be interesting to
measure exactly what this influence has been. Adding a bit of more
control to the user might contribute also to gamification. Right now
the user has only two Web Workers. It is a matter of a single click to
open more tabs in the browser, giving more Web Workers, but it would be
interesting to put everything in a single page and under our control,
to check how often this happens and under which conditions.

Finally, the implementation needs some refinement in terms of
programming and also ease of use. Tools such as Yeoman might be used
to create a generator in which the user just has to create a fitness
function, with the rest of the framework wrapped around
automatically. All this, as the data used for this paper and the paper
itself, has been published with a free license in GitHub at
\url{https://github.com/JJ/modeling-volunteer-computing}.

>>>>

In general, linking and finding correlations between user choices and
performance is an interesting avenue to explore in the future. Even if
the three previous experiments were published in a similar way, one
obtained up to 5 times more total cycles  that the one with the least
number of cycles. It is also essential to obtain volunteers as
simultaneously as possible, so it is possible that the features of the
social network in terms of real-time use will also play a big
role. Even as it is difficult to create controlled experiments in this
area, it is an interesting challenge to explore in the future.

Although we think that, in general, the results presented in this
paper are independent of the problem chosen, it is true that even if
it is a difficult problem for evolutionary algorithms, it takes a few
seconds with the right settings to solve. This makes it difficult also
for this kind of asynchronous framework, but it would be interesting
to check the performance for more computationally demanding
tasks. Besides, the two versions of the framework include as an
algorithmic variant using random population size. We do not think this
has had a big influence on the results, but it would be interesting to
measure exactly what this influence has been. Adding a bit of more
control to the user might contribute also to gamification. Right now
the user has only two Web Workers. It is a matter of a single click to
open more tabs in the browser, giving more Web Workers, but it would be
interesting to put everything in a single page and under our control,
to check how often this happens and under which conditions.

Finally, the implementation needs some refinement in terms of
programming and also ease of use. Tools such as Yeoman might be used % ¿añadir una cita o la URL http://yeoman.io/ a pie de página ?
to create a generator in which the user just has to create a fitness
function, with the rest of the framework wrapped around
automatically. All this, as the data used for this paper and the paper
itself, has been published with a free license in GitHub at
\url{https://github.com/JJ/modeling-volunteer-computing}.
